maxent model avec xvalidation (year-based test training)

### 2019-04-12 src/maxent_avec_xvalidation.Rmd
minor update to sum

#stsum <- calc(stkasc, fun=sum)
stavg <- calc(stkasc, fun = mean)
  writeRaster(stavg, (paste0("../output/maxent/predictions/", mthna, "/avg_", mthna, ".asc")), overwrite=TRUE)
  avgplot <- plot(stavg, png(paste0("../output/maxent/predictions/", mthna, "/avg_", mthna, ".png"))) 
  dev.off()

>>>>

stsum <- sum(stackavg, na.rm = TRUE)
  writeRaster(stsum, (paste0("../output/maxent/predictions/", mthna, "/sum_", mthna, ".asc")), overwrite=TRUE)
  sumplot <- plot(stsum, png(paste0("../output/maxent/predictions/", mthna, "/sum_", mthna, ".png"))) 
  dev.off()
stavg <- calc(stackavg, fun = mean, na.rm = TRUE)
  writeRaster(stavg, (paste0("../output/maxent/predictions/", mthna, "/avg_", mthna, ".asc")), overwrite=TRUE)
  avgplot <- plot(stavg, png(paste0("../output/maxent/predictions/", mthna, "/avg_", mthna, ".png"))) 
  dev.off()
